---
title: "PROPHETS"
author: "Jennifer Huellein"
date: "2023-04-19"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PROPHETS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
```

```{r setup}
library(prophets)
```

# Calculation of sample size and statistical power of the study 

Define desired variables
```{r}
delta = 1.3
alpha = 0.05
power = 0.8
rho = 0.5
alt_HR = 1.33
null_HR = 1
k = 1
lost = 0.1
model = "GBVE"
```


## Sample size calculation

```{r}
PFSr_samplesize(
  alpha = alpha,
  power = power,
  rho = rho,
  alt_HR = alt_HR,
  null_HR = null_HR,
  k = k, 
  lost = lost,
  model = model,
  verbose = TRUE)
```

## Sample size calculation using GES

```{r}
ges_PFSr_samplesize(
  ges = 0.3, 
  alpha = alpha, 
  power = power, 
  lost = lost, 
  verbose = FALSE
)
```

## Sample size calculation according to a pre-specified proportion of patients with positive PFSr

```{r}
PFSr_samplesize_proportion(
  p0 = 0.15, 
  p1 = 0.24,
  alpha = alpha, 
  beta = 0.1,
  pfsratio = 1.3, 
  lost = lost,
  verbose = TRUE
)

```

## Calculation of the statistical power of a study with a given sample size

```{r}
PFSr_power_calculate(
  sample_size = 165, 
  null_HR = null_HR,
  alt_HR = alt_HR, 
  rho = rho, 
  alpha = alpha,
  k = k, 
  model = model,
  verbose = TRUE)
```

## Calculation of the statistical power of a study with a given sample size using GES

```{r}
PFSr_power_calculation_ges(
  sample_size = 165, 
  ges = 0.3, 
  alpha = alpha,
  verbose = TRUE
)
```

# Analysis of progression free survival ratio

Load example data
```{r}
data(input)
head(input)
```

Add PFSr
```{r}
input$ratio <- input$PFS2 / input$PFS1
```

Optionally: Use modified PFS values
```{r}
data_modifiedPFS <- modify_PFS(input, delta = delta, min_pfs2 = 6)
```



## Descriptive analysis of PFSr values

### Swimmer plot

```{r}
swimmerplot_PFSr(
    input, 
    delta = delta)
```


### Correlation between PFS1 and PFS2

```{r}
plot_correlation_PFS(
  input, 
  delta = delta,
  log_scale = FALSE
)
```

### Cumulative hazard ratio

```{r}
plot_cumHaz(
  input,  
  selected_PFS = c("PFS1", "PFS2") 
)
```

### Plot Weibull

```{r}
plot_weibull(input)
```


## Methods for calculation of significant PFSr


### Count-based method

```{r}
res_countPFSr <- count_PFSr(
  data = input,
  delta = delta,
  prob = 0.5
  )

res_countPFSr
```


### Kaplan-Meier-based method

```{r}
res_kaplanMeierPFSr <- kaplanMeier_PFSr(
  data = input,
  delta = delta,
  plot = TRUE
)

res_kaplanMeierPFSr
```


### Parametric method

```{r}
res_parametricPFSr <- parametric_PFSr(
  data = input,
  delta = delta
)

res_parametricPFSr
```


### Midrank-based method

```{r}
res_midrankPFSr <- midrank_PFSr(
  data = input, 
  delta = delta
)

res_midrankPFSr
```


### Summary of all methods

```{r}
res_summary <- prophets_summary(
  data = input,
  delta = delta
)

res_summary
```

